

\textbf{Krzysztof}

In the project's execution, I initiated a GitHub repository, organized the project's structure for efficient code management, and maintained code quality through the review of Pull/Merge requests. I also crafted Dockerfiles for the prediction-api and prediction-ui components and managed the deployment on Cloud Build and Cloud Run in a cloud environment. Furthermore, I created Figure 1 and provided an in-depth account of the machine learning application's design and deployment in the documentation. Towards the project's conclusion, I oversaw comprehensive testing to ensure the application's overall functionality.
 
\textbf{Chigozie}
We cooperated collectively also in writing the steps of the pipeline. I assisted in building the triggers within the CI-CD pipeline in the cloud build. And made sure everything in the trigger was running smoothly.

\textbf{Vishal}
I started a project with Krzysztof on Git Hub and made sure everything was organized. I set up some technical parts to run online and worked on making our tool guess things correctly. Me and Chigozie worked on trigger and I also made sure the part where users enter information was easy to use with the stroke prediction. 

\textbf{Xavier}
My primary focus was on the user interface, where users filled out essential forms. Within this interface, I played a key role in encoding the user-provided input into variables that were subsequently employed in our stroke prediction process. Additionally, I contributed to the adaptation and refinement of the Kaggle-provided models, ensuring they delivered accurate predictions based on the user's input variables.


\textbf{Kyriakos} For this project I was in charge of writing the Vertex AI code for training two models, making sure that they surpass a certain threshold. Furthermore, I prepared the function to compare the two models and choose the best one. Also, I helped writing some parts of the report and transforming it to the LaTeX format.
